Constant-round Blind Classical Verification of Quantum Sampling

### 2020-10-04 introduction.tex
Fix intro/prelim action items

\Ethan{This paragraph is new and has to be checked}
Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however,
it is still unclear how to construct a CVQC protocol for $\SampBQP$.
A protocol for classical sampling problems is usually obtained from that of decision problems,
by fixing a seed for pseudorandomness then computing the output bit-by-bit.
This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements.
Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
since it is unclear how to use the usual trick of running many copies of the protocol then applying the Chernoff bound.

>>>>

\Ethan{This paragraph is new and has to be checked}
Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however,
it is still unclear how to construct a CVQC protocol for $\SampBQP$.
In the context of delegating \emph{classical} sampling problems,
there is a simple reduction to that of decision problems.
Namely, the verifier fixes a seed for pseudorandomness and send it to the prover,
then the sampling outcome can be computed deterministically bit-by-bit using this pseudorandomness.
Unfortunately, this de-randomization trick does not work for delegation of $\SampBQP$, as quantum computation is inherently random.
\Ethan{Next part needs discussion on context Ie. protocol or local computation}
Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
since it is unclear how to apply the usual trick of running many copies of the protocol then applying the Chernoff bound.

### 2020-10-04 preliminaries.tex
Fix intro/prelim action items

We define $\SampBQP$ based on \cite{aaronson_2013, aaronson_arkhipov_2011}.
\Ethan{Tried to explain better}
This complexity class is meant to model feasible quantum computations.
It is worth noting that quantum states live in a Hilbert space which is continuous,
so it is likely that any physical implementation of quantum computing would naturally involve some sort of errors.
\cite{aaronson_arkhipov_2011} gives an argument from the physical implementation perspective that this error should be inverse polynomial.

>>>>

We define $\SampBQP$ based on \cite{aaronson_2013, aaronson_arkhipov_2011}.
\Ethan{Tried to explain better}
This complexity class is meant to model feasible quantum computations.
As quantum states live in a continuous Hilbert space,
it is likely that any realization of quantum computing would suffer from natural noise and inaccuracies.
An argument from the physical implementation perspective that this error should be on an inverse polynomial scale is given in \cite{aaronson_arkhipov_2011}.
As a result, $\SampBQP$ is correspondingly stated to allow inverse-polynomial errors.
